fig4

### 2020-03-04 analysis/figure-3.Rmd
new fig 1

>>>>

```{r gon}
# pca
charpca <- subsetmakepca("gonads", charlevels, sexlevels)	
charfviz <- makefvizdf("gonads", charlevels, sexlevels)

a <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = "none", 
        legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = "gonad")

b <- plotfriz(charfviz) + labs(subtitle = "gonad") +
  #ylim(-250000,500000) + xlim(-250000,500000) + 
  theme(axis.text = element_blank())

plot_grid(a,b)

head(charpca)

ggplot(charpca, aes(x = PC1, y = PC2, shape = tissue, color = treatment )) +	
    geom_point(size = 1)  +	
  stat_ellipse( ) +
    theme_B3() +
  scale_color_manual(values = colorschar)

ggplot(charpca, aes(x = PC1, y = PC3, shape = tissue, color = treatment )) +	
    geom_point(size = 1)  +	
  stat_ellipse( ) +
    theme_B3() +
  scale_color_manual(values = colorschar) +
  facet_wrap(~sex)

ggplot(charpca, aes(x = PC1, y = PC3, shape = tissue, color = treatment )) +	
    geom_point(size = 1)  +	
  stat_ellipse( ) +
    theme_B3() +
  scale_color_manual(values = colorschar) +
  facet_wrap(~sex)
```

### 2020-03-04 analysis/figure-4.Rmd
new fig 1

@@

  df  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts)

@@

candidatevsd <- returnvsds(candidategenes)

@@

```{r savefiles}
write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
```

>>>>

DEGs <- read_csv("../results/DEGs-char.csv")  %>%
  dplyr::filter(comparison != "control_bldg") %>%
  dplyr::distinct(gene)  %>% arrange(gene) %>%
  filter(!grepl("LOC", gene)) #%>% 
  #pull(gene)

HUGO <- read_table("../metadata/HUGOGeneNomenclature.txt")
names(HUGO)[1] <- "all"
HUGO$gene <- sapply(strsplit(HUGO$all,'\t'), "[", 3)
HUGO$name <- sapply(strsplit(HUGO$all,'\t'), "[", 4)
HUGO <- HUGO %>%distinct(gene,name)

DEGsHUGO <- inner_join(DEGs, HUGO, by = "gene") %>% pull(gene)

parentalbehavior <- read_table("../results/goterms/parentalbehavior.txt")
names(parentalbehavior)[1] <- "allGO"
parentalbehavior$id <- sapply(strsplit(parentalbehavior$allGO,'\t'), "[", 1)
parentalbehavior$gene <- sapply(strsplit(parentalbehavior$allGO,'\t'), "[", 2)
parentalbehavior$name <- sapply(strsplit(parentalbehavior$allGO,'\t'), "[", 3)
parentalbehavior$GO <- sapply(strsplit(parentalbehavior$allGO,'\t'), "[", 6)
parentalbehavior$allGO <- NULL
parentalbehaviorgenes <- parentalbehavior %>% 
  mutate(gene = str_to_upper(gene)) %>%  pull(gene)
parentalbehaviorgenes

@@

  df  <- allvsd %>%
    dplyr::filter(!grepl("control", samples)) %>%
    dplyr::filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts)

@@

candidatevsd <- returnvsds(candidategenes)
#DEGvsd <- returnvsds(DEGsHUGO) too big 1G
parentalvsd <- returnvsds(parentalbehaviorgenes)
```

@@

```{r savefiles}
write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
write.csv(parentalvsd, "../../musicalgenes/data/parentalcounts.csv")
